---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Build Status](https://travis-ci.org/rzhou14/freebird.svg)](https://travis-ci.org/rzhou14/freebird)
[![Package-License](http://img.shields.io/badge/license-GPL%20(%3E=2)-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html)
<!--
[![CRAN Version Badge](http://www.r-pkg.org/badges/version/freebird)](https://cran.r-project.org/package=freebird)
[![CRAN Status](https://cranchecks.info/badges/worst/freebird)](https://cran.r-project.org/web/checks/check_results_freebird.html)
[![RStudio CRAN Mirror's Monthly Downloads](http://cranlogs.r-pkg.org/badges/freebird?color=brightgreen)](http://www.r-pkg.org/pkg/freebird)
[![RStudio CRAN Mirror's Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/freebird?color=brightgreen)](http://www.r-pkg.org/pkg/freebird)
-->
[![Coverage status](https://codecov.io/gh/rzhou14/freebird/branch/master/graph/badge.svg)](https://codecov.io/github/rzhou14/freebird?branch=master)


# freebird

The goal of `freebird` is to estimation and perform inference for High Dimensional Median Analysis.

## Installation

If you have a compiler installed on your computer, then you can install the development version
of freebird from GitHub by using:

```{r gh-install, eval = FALSE}
if(requireNamespace("devtools")) install.packages("devtools")
devtools::install_github("rzhou14/freebird")
```

We soon hope to have it ready for [CRAN](https://CRAN.R-project.org).

<!--- with:

``` r
install.packages("freebird")
```

-->

## Usage

To use `freebird`, please load the package with:

```{r load-pkg}
library("freebird")
```


## Authors

Ruixuan Zhou and Dave Zhao

Special Thanks to James Balamuta for giving up his lunch hour!

## License

GPL (>= 2)
